A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-10-03 paper1.tex
last Fabio

{\bf Galaxy clusters are the rarest and largest gravitationally-collapsed
  objects in the Universe and form at sites of constructive interference of long
  waves in the primordial density fluctuations. Clusters reach radial extends of
  a few Mpc and total masses $M \sim (10^{14} - 10^{15}) M_{\odot}$, of which
  galaxies, hot ($1-10$~keV) gas and dark matter (DM) contribute roughly 5, 15
  and 80 per cent, respectively. If the thermal properties of the intracluster medium
  (ICM) were solely determined by the gravity of the system, then clusters would
  obey self-similar scaling relations \citep{1986MNRAS.222..323K}.  However,
  X-ray observations have demonstrated that self-similarity is broken,
  especially at low-mass scales (see e.g., \citealp{2005RvMP...77..207V} for a
  review). Apparently the energy input from non-gravitational processes
  associated with galaxy formation have a larger influence in smaller systems,
  i.e., at scales of galaxy groups.

  The central cooling time of the X-ray emitting gas in galaxy clusters and
  groups is bimodally distributed. Approximately half of all systems have
  radiative cooling times of less than 1~Gyr and establish a population of cool
  core clusters (CCC) while others have cooling times that can be longer than
  the age of the Universe, forming the non-cool core cluster (NCCC) population
  \citep{2009ApJS..182...12C,2010A&A...513A..37H}. Several physical processes
  have been proposed to be responsible for balancing radiative cooling of the
  low-entropy gas at the centers of CCCs. In particular feedback by active
  galactic nuclei (AGN) has come into the focus of recent research
  \citep{2007ARA&A..45..117M, 2012NJPh...14e5023M} owing to the self-regulated
  nature of the proposed feedback and observational correlations between radio
  activity and central entropy (which is a proxy for a small cooling time). The
  underlying physical processes responsible for the heating include dissipation
  of mechanical heating by outflows, lobes, or sound waves from the central AGN
  \citep[e.g.,][]{2001ApJ...554..261C, 2002Natur.418..301B, 2002ApJ...581..223R,
    2012MNRAS.424..190G} or cosmic-ray heating: streaming cosmic rays excite
  Alfv\'en waves on which they resonantly scatter \citep{1969ApJ...156..445K}.
  Damping of these waves transfers cosmic ray energy and momentum to the cooling
  plasma \citep{1991ApJ...377..392L, 2008MNRAS.384..251G, 2011A&A...527A..99E,
    2013MNRAS.434.2209W}, heating it at a rate that balances radiative cooling
  on average at each radius while explaining the observed temperature floor in
  CCCs by thermal stability of the heating mechanism
  \citep{2013arXiv1303.5443P}.

@@

\begin{table} 
\begin{center}
\caption{Number of halos in the final cluster sample}
\medskip
\begin{tabular}{cc}
\hline
\phantom{\Big|}
redshift $z$ & number of halos \\
\hline\\[-0.5em]
 0.0~~ &  13763\\
 0.05 &  13103\\
 0.1~~ &  12398\\
 0.16 & 11419\\
 0.2~~ &  10783\\ 
 0.27 & ~~9772\\
 0.32 & ~~9039\\
 0.37 & ~~8197\\
 0.4~~ &   ~~7789\\
 0.47 & ~~6957\\
 0.53 & ~~6079\\ 
 0.61 &  ~~5187\\ 
 0.69 & ~~4288\\
 0.78 &  ~~3372\\ 
 0.89 & ~~2575\\
 1.0~~ &  ~~1803\\[0.5em]
\hline
\end{tabular}
\label{tab:z}
\end{center}
\footnotesize{Note. We show the number of halos in our MultiDark snapshots at redshift $z$ for $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$. }
\end{table}

@@

{\bf As a cautionary remark, we emphasize that our model is only valid within
  $R_{500}$ and more work is needed to extrapolate it to larger cluster
  radii. Those cluster regions are characterized by a steadily increasing level
  of kinetic-to-thermal pressure support \citep[e.g.,][]{2009ApJ...705.1129L,
    2012ApJ...758...74B}, density clumping \citep{2011ApJ...731L..10N,
    2012arXiv1209.4082B}, and asphericity and ellipticity of the halo
  morphologies \citep{2012arXiv1209.4082B}, in particular beyond the virial
  radius where the filamentary cosmic web connects to the cluster interiors.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SZ scaling relations}
\label{sec:5}
In the left panel of Fig.~\ref{fig:SZ_M}, we compare the $Y_{\rmn{SZ}}-M_{500}$
relation of our model (following \citealp{2012ApJ...758...74B}, equation~3) with
the observed scaling relation by the \cite{2013arXiv1303.5080P}. {\bf We use the
  \emph{Planck} COSMO sample, which is Malmquist-bias corrected and has a median
  redshift of $0.18$, and compare this to our $z=0.2$ relation}. Our model
reproduces the normalization of the scaling relation remarkably well, except for
the high-mass end where our simulations have a weaker constraining power due to
the smaller box size in comparison to the survey volume of {\em Planck}.  {\bf
  However, the slope of our $Y_{\rmn{SZ}}-M_{500}$ relation ($1.59\pm0.01$) is
  shallower in comparison to the self-similar slope ($5/3$) as well as the
  observed slope of the \emph{Planck} COSMO sample. We can analytically
  understand the cluster-mass scaling of our model by considering its
  mass-dependent quantities, namely $Y_{\rmn{SZ}}\propto M_{500} f_{\rmn{gas}}
  T \propto M_{500}^{1.595}$. In particular, we can trace back the
  shallower slope to the adopted temperature scaling of our model
  ($T\approx T_{\rmn{ci}}\propto M_{500}^{0.46}$), which includes the cluster core region
  and yields a shallower mass scaling in comparison to the self-similar
  expectation ($T\propto M_{500}^{2/3}$). The temperature scaling is only
  partially countered by the scaling of the gas mass fraction with cluster mass,
  $f_{\rmn{gas}}\propto M_{500}^{0.135}$. To improve upon this, we would have to
  account for a slightly steeper temperature-mass scaling (e.g., using a
  centrally excised temperature scaling, see \citealt{2010MNRAS.406.1773M}) in
  the outer cluster parts that are of relevance for the SZ flux, as explained in
  Sect.~\ref{sec:Xscaling}. }  We find a scatter of $\sigma_{yx} \approx 0.11$
which compares well with the \emph{Planck} result of $\sigma_{yx} \approx
0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling relations for
different redshifts.

\begin{figure*} 
\centering
\includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
\caption{{\bf Comparison of our SZ scaling relations (grey triangles) with
    data. The bottom panels show the relative difference to the observational
    scaling relations. \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at
    $z=0.2$ with the {\em Planck} data \citep[blue,][]{2013arXiv1303.5080P},
    which have a median redshift of about $0.18$.  The black crosses represent
    the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin
    (indicated by horizontal error bars), and the vertical error bars represent
    the standard deviation within a bin. \emph{Right.} We compare our
    $Y_{\rmn{SZ}}-M$ relation at $z=0.53$ with the ACT sample
    \protect\citep[blue,][]{2013JCAP...07..008H} assuming a self-similar
    redshift evolution.}}
\label{fig:SZ_M}
\end{figure*}

\begin{table} 
\begin{center}
\caption{$Y_{\rmn{SZ}, 500}-M_{500}$ scaling relations.}
\medskip
\begin{tabular}{cccc}
\hline
\phantom{\Big|}
redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
\hline\\[-0.5em]
 0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
 0.1   & $-27.74\pm0.07$ & $1.59\pm0.01$ & 0.109\\
 0.18 & $-27.73\pm0.08$ & $1.59\pm0.01$ & 0.109\\
 0.2   & $-27.65\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
 0.4   & $-27.57\pm0.10$ & $1.59\pm0.01$ & 0.108\\ 
 0.61 & $-27.50\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
 0.78 & $-27.15\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
 1      & $-27.01\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
\hline
\end{tabular}
\label{tab:YSZfits}
\end{center}
\footnotesize{Note. Scaling relations are reported in the form of $\log_{10}~(E(z)^{-2/3}~Y_{\rmn{SZ},500}~/~h_{70}^{-2.5}~\rmn{Mpc}^{2})=A+B~\log_{10}~(M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$. The relation scatter $\sigma_{yx}$ is also shown.}
\end{table}

{\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
  to the ACT sample overlapping with the Sloan Digital Sky Survey stripe 82
  \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$. Again,
  the slope of our modeled scaling relation is somewhat shallower in comparison
  to the observed slope. Most strikingly, there appears to be a 30 per cent
  offset of the scaling relations, which could be due to a number of reasons. On
  the data side, these could include possible selection effects of the different
  cluster samples or possible biases associated with density clumping and/or
  non-thermal pressure contributions inherited from the X-ray informed
  post-processing that was employed by the ACT Collaboration to construct their
  $Y_{500}$ estimates. However, this could also indicate that our presented
  model is too simplistic to capture the rich cluster physics and potentially
  may even signal deviations from the assumed self-similar redshift evolution
  (since ACT sample probes on average higher redshift and less massive clusters
  in comparison to the {\em Planck} sample). Overall, there is reasonable
  agreement between our phenomenological model and the SZ data of the
  \emph{Planck} and ACT collaborations.}

@@

  However, there are some notable deviations among the different observational
  scaling relations and our model, which may either point to observational
  sample selection effects that are not accounted for or missing complexity of
  our model. This model was specifically constructed to provide a reliable
  description of the gas density, which necessarily implies a great match of the
  resulting mock X-ray observables to data (scaling relations and luminosity
  functions) as well as to the low-redshift and massive cluster sample probed by
  {\em Planck}. However, we note that our model has a somewhat shallower slope
  of the $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
  deviations of self-similarity on small scales become weaker on the larger
  scales probed through the SZ effect. Moreover, our model overpredicts the
  normalization of the ACT $Y_{\rmn{SZ}}-M_{500}$ relation (at $z=0.53$) by
  about 30 per cent. This could either indicate possible selection effects of
  the different cluster samples or may even signal a deviation from the assumed
  self-similar redshift evolution.

@@

\del{
The study of the (non-)thermal emission in galaxy clusters provides
important information on structure formation process and on 
fundamental characteristics of our Universe. This field is at a 
crucial point of its development thanks to the very low sensitivity of present and future-generation 
instruments such as LOFAR\footnote{www.lofar.org}, \emph{e}ROSITA\footnote{www.mpe.mpg.de/eROSITA}, 
ASTRO-H\footnote{astro-h.isas.jaxa.jp} and CTA\footnote{www.cta-observatory.org}, to name but a few. 
Therefore, it is important to provide prospects for future surveys and
to understand in which way they can improve our current knowledge.
To this end, a complete cosmological mock sample of galaxy
clusters is needed. This can be realized either using analytical 
expressions for the cluster mass function (e.g., \citealp{2001MNRAS.321..372J}) or cosmological cluster 
simulations. In this work, we make use of the recent MultiDark $N$-body
simulation (\citealp{2011arXiv1104.5130P}; www.multidark.org).
%
Our main motivation to build such a mock catalog has been to predict the 
non-thermal emission at radio frequencies of a cosmological 
complete sample of galaxy clusters. This is presented in a companion 
paper (\citealp{paper2}; hereafter Paper~II). As described in Paper~II, for 
any given cluster, fundamental ingredients for the non-thermal emission 
model are the mass and gas density distribution. The MultiDark 
simulation used here is a $N$-body, \emph{dark matter (DM)-only} simulation and, 
therefore, does not contain any information on the intra-cluster medium (ICM) gas  
distribution. A cosmological complete sample of clusters can 
only be obtained from $N$-body simulations as hydrodynamical
simulations of such large volumes are computationally too expensive.
Therefore, we need a method to determine the ICM properties
of any given cluster from its total mass. 
%
ACT SZ:
This sample has a median redshift of 0.58 with
  rms of 0.28. \cite{2013JCAP...07..008H} provides $Y_{\rmn{SZ}}$ within
  $R_{500}$, which median, $0.42$~h$_{70}^{-1}$~Mpc, is almost half of ours at
  the MultiDark snapshot $z=0.61$. Therefore, we use an aperture of
  $0.42$~h$_{70}^{-1}$~Mpc to calculate our $Y_{\rmn{SZ, ACT}}$.  The fact that
  our $R_{500}$ does not compare well with the ACT values, while it does with
  \emph{Planck}, may be explained as follows. We adopt the ACT measurements
  derived from the 148~GHz data assuming that the cluster pressure is described
  by the universal profile of \cite{2010A&A...517A..92A}. In contrast,
  \cite{2013arXiv1303.5080P} derived $R_{500}$ from X-ray measurements of
  $M_{500}$, similarly to our approach of constructing gas densities from an
  X-ray sample of clusters.
%
Summarizing, our SZ scaling relations compare very well to the result from
the \emph{Planck} collaboration. However, the comparison with the SPT and 
ACT samples is not as straightforward due to the different selection function 
of these telescopes with respect to \emph{Planck}, which results in a much
more (redshift) non-homogeneous sample. Nevertheless, our mock clusters 
can reproduce well the median SPT and ACT populations. A more detailed
comparison would need the generation of light-cone mock catalogs,
including instrumental effects, which is beyond the scope of this 
work.}

>>>>

{\bf Galaxy clusters are the rarest and largest gravitationally-collapsed
  objects in the Universe and form at sites of constructive interference of long
  waves in the primordial density fluctuations. Clusters reach radial extends of
  a few Mpc and total masses $M \sim (10^{14} - 10^{15}) M_{\odot}$, of which
  galaxies, hot ($1-10$~keV) gas and dark matter (DM) contribute roughly 5, 15
  and 80 per cent, respectively. If the thermal properties of the intracluster medium
  (ICM) were solely determined by the gravity of the system, then clusters would
  obey self-similar scaling relations \citep{1986MNRAS.222..323K}.  However,
  X-ray observations have demonstrated that self-similarity is broken,
  especially at low-mass scales (see, e.g., \citealp{2005RvMP...77..207V} for a
  review). Apparently the energy input from non-gravitational processes
  associated with galaxy formation have a larger influence in smaller systems,
  i.e., at scales of galaxy groups.

  The central cooling time of the X-ray emitting gas in galaxy clusters and
  groups is bimodally distributed. Approximately half of all systems have
  radiative cooling times of less than 1~Gyr and establish a population of cool
  core clusters (CCCs) while others have cooling times that can be longer than
  the age of the Universe, forming the non-cool core cluster (NCCC) population
  \citep{2009ApJS..182...12C,2010A&A...513A..37H}. Several physical processes
  have been proposed to be responsible for balancing radiative cooling of the
  low-entropy gas at the centers of CCCs. In particular feedback by active
  galactic nuclei (AGN) has come into the focus of recent research
  \citep{2007ARA&A..45..117M, 2012NJPh...14e5023M} owing to the self-regulated
  nature of the proposed feedback and observational correlations between radio
  activity and central entropy (which is a proxy for a small cooling time). The
  underlying physical processes responsible for the heating include dissipation
  of mechanical heating by outflows, lobes, or sound waves from the central AGN
  \citep[e.g.,][]{2001ApJ...554..261C, 2002Natur.418..301B, 2002ApJ...581..223R,
    2012MNRAS.424..190G} or cosmic-ray heating: streaming cosmic rays excite
  Alfv\'en waves on which they resonantly scatter \citep{1969ApJ...156..445K}.
  Damping of these waves transfers cosmic ray energy and momentum to the cooling
  plasma \citep{1991ApJ...377..392L, 2008MNRAS.384..251G, 2011A&A...527A..99E,
    2013MNRAS.434.2209W}, heating it at a rate that balances radiative cooling
  on average at each radius while explaining the observed temperature floor in
  CCCs by thermal stability of the heating mechanism
  \citep{2013arXiv1303.5443P}.

@@

\begin{table} 
\begin{center}
\caption{Number of halos in the final cluster sample}
\medskip
\begin{tabular}{cc}
\hline
\phantom{\Big|}
redshift $z$ & number of halos \\
\hline\\[-0.5em]
 0.0~~ &  13763\\
 0.05 &  13103\\
 0.1~~ &  12398\\
 0.16 & 11419\\
 0.18 &  11106\\
 0.2~~ &  10783\\ 
 0.27 & ~~9772\\
 0.32 & ~~9039\\
 0.37 & ~~8197\\
 0.4~~ &   ~~7789\\
 0.47 & ~~6957\\
 0.53 & ~~6079\\ 
 0.61 &  ~~5187\\ 
 0.69 & ~~4288\\
 0.78 &  ~~3372\\ 
 0.89 & ~~2575\\
 1.0~~ &  ~~1803\\[0.5em]
\hline
\end{tabular}
\label{tab:z}
\end{center}
\footnotesize{Note. We show the number of halos in our MultiDark snapshots at redshift $z$ for $M_{200}\geq1\times10^{14}$~$h^{-1}$~M$_{\odot}\approx1.4\times10^{14}$~$h_{70}^{-1}$~M$_{\odot}$. }
\end{table}

@@

%{\bf As a cautionary remark, we emphasize that our model is only valid within
%$R_{500}$ and more work is needed to extrapolate it to larger cluster
%radii, \qc{particularly for the thermal modeling}.
{\bf As a cautionary remark, \qc{we emphasize that our model is built
to be valid within $R_{500}$ and more work is needed to extrapolate it to 
larger cluster radii, particularly for the thermal modeling}.
Those cluster regions are characterized by a steadily increasing level
of kinetic-to-thermal pressure support \citep[e.g.,][]{2009ApJ...705.1129L,
2012ApJ...758...74B}, density clumping \citep{2011ApJ...731L..10N,
2012arXiv1209.4082B}, and asphericity and ellipticity of the halo
morphologies \citep{2012arXiv1209.4082B}, in particular beyond the virial
radius where the filamentary cosmic web connects to the cluster interiors.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{SZ scaling relations}
\label{sec:5}

\begin{figure*} 
\centering
\includegraphics[width=0.48\textwidth]{figures/sz_m.eps}
\includegraphics[width=0.48\textwidth]{figures/sz_m_ACT.eps}
\caption{{\bf Comparison of our SZ scaling relations (grey triangles) with
    data. The black crosses represent
    the $Y_{\rmn{SZ}}$ median values of our sample for a given mass bin
    (indicated by horizontal error bars), and the vertical error bars represent
    the standard deviation within a bin. 
    The bottom panels show the relative difference to the observational
    scaling relations.
    \emph{Left.}  We compare our $Y_{\rmn{SZ}}-M$ relation at
    $z=0.18$ with the {\em Planck} data \citep[blue,][]{2013arXiv1303.5080P},
    which have a median redshift of about $0.18$. \emph{Right.} We compare our
    $Y_{\rmn{SZ}}-M$ relation at $z=0.53$ with the ACT sample
    \protect\citep[blue,][]{2013JCAP...07..008H} assuming a self-similar
    redshift evolution.}}
\label{fig:SZ_M}
\end{figure*}

In the left panel of Fig.~\ref{fig:SZ_M}, we compare the $Y_{\rmn{SZ}}-M_{500}$
relation of our model (following \citealp{2012ApJ...758...74B}, equation~3) with
the observed scaling relation by the \cite{2013arXiv1303.5080P}. {\bf We use the
  \emph{Planck} COSMO sample, which is Malmquist-bias corrected and has a median
  redshift of $0.18$, and compare this to our $z=0.18$ relation}. Our model
reproduces the normalization of the scaling relation remarkably well, except for
the high-mass end where our simulations have a weaker constraining power due to
the smaller box size in comparison to the survey volume of {\em Planck}.  {\bf
  However, the slope of our $Y_{\rmn{SZ}}-M_{500}$ relation ($1.59\pm0.01$) is
  shallower in comparison to the self-similar slope ($5/3$) as well as the
  observed slope of the \emph{Planck} COSMO sample. We can analytically
  understand the cluster-mass scaling of our model by considering its
  mass-dependent quantities, namely $Y_{\rmn{SZ}}\propto M_{500} f_{\rmn{gas}}
  T \propto M_{500}^{1.595}$. In particular, we can trace back the
  shallower slope to the adopted temperature scaling of our model
  ($T\approx T_{\rmn{ci}}\propto M_{500}^{0.46}$), which includes the cluster core region
  and yields a shallower mass scaling in comparison to the self-similar
  expectation ($T\propto M_{500}^{2/3}$). The temperature scaling is only
  partially countered by the scaling of the gas mass fraction with cluster mass,
  $f_{\rmn{gas}}\propto M_{500}^{0.135}$. To improve upon this, we would have to
  account for a slightly steeper temperature-mass scaling (e.g., using a
  centrally excised temperature scaling, see \citealt{2010MNRAS.406.1773M}) in
  the outer cluster parts that are of relevance for the SZ flux, as explained in
  Sect.~\ref{sec:Xscaling}. }  We find a scatter of $\sigma_{yx} \approx 0.11$
which compares well with the \emph{Planck} result of $\sigma_{yx} \approx
0.08$. In Table~\ref{tab:YSZfits}, we report our SZ scaling relations for
different redshifts.

\begin{table} 
\begin{center}
\caption{$Y_{\rmn{SZ}, 500}-M_{500}$ scaling relations.}
\medskip
\begin{tabular}{cccc}
\hline
\phantom{\Big|}
redshift $z$ & $A$ & $B$ & $\sigma_{yx}$ \\
\hline\\[-0.5em]
 0      & $-27.93\pm0.07$ & $1.60\pm0.01$ & 0.109\\
 0.1   & $-27.75\pm0.07$ & $1.59\pm0.01$ & 0.109\\
 0.18 & $-27.75\pm0.08$ & $1.59\pm0.01$ & 0.109\\
 0.2   & $-27.68\pm0.08$ & $1.59\pm0.01$ & 0.109\\ 
 0.4   & $-27.62\pm0.10$ & $1.59\pm0.01$ & 0.108\\
 0.53 & $-27.67\pm0.11$ & $1.59\pm0.01$ & 0.109\\
 0.61 & $-27.59\pm0.13$ & $1.59\pm0.01$ & 0.109\\ 
 0.78 & $-27.26\pm0.18$ & $1.58\pm0.01$ & 0.109\\ 
 1      & $-27.16\pm0.26$ & $1.58\pm0.02$ & 0.109\\[0.5em] 
\hline
\end{tabular}
\label{tab:YSZfits}
\end{center}
\footnotesize{Note. Scaling relations are reported in the form of $\log_{10}~(E(z)^{-2/3}~Y_{\rmn{SZ},500}~/~h_{70}^{-2.5}~\rmn{Mpc}^{2})=A+B~\log_{10}~(M_{500}~/~h_{70}^{-1}~\rmn{M_{\odot}})$. The relation scatter $\sigma_{yx}$ is also shown.}
\end{table}

{\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
  to the \qc{recent Atacama Cosmology Telescope (ACT) sample} \citep{2013JCAP...07..008H}, 
  which has a median redshift of $z=0.53$. 
  Again, the slope of our modeled scaling relation is somewhat shallower in comparison
  to the observed slope. Most strikingly, there appears to be a 30 per cent
  offset of the scaling relations, which could be due to a number of reasons. On
  the data side, these could include possible selection effects of the different
  cluster samples or possible biases associated with density clumping and/or
  non-thermal pressure contributions inherited from the X-ray informed
  post-processing that was employed by the ACT Collaboration to construct their
  $Y_{500}$ estimates. This could also indicate that our presented
  model is too simplistic to capture the rich cluster physics and potentially
  may even signal deviations from the assumed self-similar redshift evolution
  (since ACT sample probes on average higher redshift and less massive clusters
  in comparison to the {\em Planck} sample). 
  \qc{However, note that our scaling relation at $z=0.53$ ($A=-27.67\pm0.11$, $B=1.59\pm0.01$) 
  is perfectly compatible within the errors with the one derived from the ACT sample 
  ($A=-28.59\pm2.26$, $B=1.65\pm0.15$).  
  Therefore, we conclude that overall} there is reasonable
  agreement between our phenomenological model and the SZ data of the
  \emph{Planck} and ACT collaborations.}

@@

%However, there are some notable deviations among the different observational
  However, there are \qc{some deviations} among the different observational
  scaling relations and our model, which may either point to observational
  sample selection effects that are not accounted for or missing complexity of
  our model. This model was specifically constructed to provide a reliable
  description of the gas density, which necessarily implies a great match of the
  resulting mock X-ray observables to data (scaling relations and luminosity
  functions) as well as to the low-redshift and massive cluster sample probed by
  {\em Planck}. However, we note that our model has a somewhat shallower slope
  of the $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
  deviations of self-similarity on small scales become weaker on the larger
  scales probed through the SZ effect. Moreover, our model overpredicts the
  normalization of the ACT $Y_{\rmn{SZ}}-M_{500}$ relation (at $z=0.53$) by
  about 30 per cent. This could either indicate possible selection effects of
  the different cluster samples or may even signal a deviation from the assumed
  self-similar redshift evolution. \qc{Nevertheless, we stress that our scaling relation
  is still compatible within the errors of the ACT one.}

@@
